---
title: Effective table design with R and DT
date: 2017-07-20 00:00:00 Z
categories:
- data-analysis
- data-visualisation
- communication
tags:
- R
layout: post
author: Jose A. Dianes
comments: true
---

>>> Intro to DT 
>>> About Stephen Few (where to put him in the dataviz spectrum) and Show me the Numbers book (the best one, less opinionated, right to business of his books, recommended)

## Business Intelligence and Exploratory Data Anlysis

## When to use tables  

>>> (p44). 

## Hello, DT  

### Our dataset

**esoph**: consumption header for two columns, repeated age groups as merged cells.  

```{r}
help(esoph)
```

```{r}
head(esoph)
```

```{r}
str(esoph)
```



### Install DT

```{r}
# install.packages("DT")
library(DT)
```

### The DT default table  


```{r}
datatable(esoph)
```

## Table design best practices with DT  

>>> (p158)

### Table components  

```{r}
colnames = c("Age group", "Alcohol consumption", "Tobacco consumption", "Number of cases", "Number of controls" )
datatable(esoph, colnames=colnames)
```

>>> (p155)  

### Delineating columns and rows  

### Arranging data  

### Formating text  

### Summarising values  

### Page information   

## Conclusions  

>>> BI vs journalism and other forms of communication. It's all about the audience.
>>> Get the source code  

Other interesting core R datasets:   
- Orange    
- PlantGrowth, ToothGrowth: they are typical treatment effect datasets. Good for learning how to use R for research.  
- UCBAdmissions: a 3d table that might be an interesting project for DT.  
- UKDriverDeaths: do some boxplots in time to study distribution trends.    


